Adopting agile in the large: motivations, success factors and challenges

### 2013-12-23 journal/article.tex
Explanation for coding test.

The metric of matching themes measures how well the independent researchers are
able to induct similar codes from the source material. As codes are inducted it
is likely that two researchers label similar quotes differently. To overcome
this problem we defined higher level themes under which the individual codes
were organized. Through discussion we made decisions on whether differently
labeled codes could be organized under the same theme or not. Table
\ref{table:codingexperiment} presents the total number of themes the researchers
found in each document, and how many of the themes were matching. We concluded
that on average two of three themes that one researcher finds are similarly
found by the other researcher, but one of three themes are not found by the
other researcher.

@@

>>>>

The metric of matching themes measures how well the independent researchers are
able to induct similar codes from the source material. As codes are inducted it
is likely that two researchers label similar quotes differently. To overcome
this problem we defined higher level themes under which the individual codes
were organized. Through discussion we made decisions on whether differently
labeled codes could be organized under the same theme or not. Table
\ref{table:codingexperiment} presents the total number of themes the researchers
found in each document, and how many of the themes were matching. We concluded
that on average two of three themes that one researcher finds are similarly
found by the other researcher, but one of three themes is not found by the
other researcher.

The metric of quotation overlap measures how well the quotations for similar
codes match between two independent researchers. The intent is to measure how
codes that are deemed similar by their names match in the actual quoted text. On
a scale of 0 to 3 we evaluated the quoted text of codes in each theme that
matched for both researchers, as described in the previous paragraph. A score of
3 was given for matching codes whose quotation content was virtually the same
for both researchers. A score of 2 was given if the quotations were mostly the
same, but other researcher had included one text passage that the other had
missed. A score of 1 was given if roughly half of the quotations were the same.
If the quotations had less similarity than this a score of 0 was given. One code
provided typically 1 to 3 quotations per document. The quotation overlap score
was counted including only codes that had matching themes. We concluded that the
average quotation overlap score was 2.2.

@@

Combining the quotation overlap result and the result that inductive coding
yielded similar themes with a factor of two thirds, we conclude that two
different researchers should agree completely on at least half of the quotations
in the source material of our study. This agreement includes both that the
researchers select the same text passage as a quotation, and that researchers
agree with the meaning of the quotation. Further interpretation of the
quotations and codes will still remain a subjective matter.
